### 2011-02-09 paper/fitnessEvaluation.tex
Finished linearInterp figure

@@

\edit{Put this in there somewhere:}

To be as fair as possible when obtaining the results presented in
\secref{results}, we picked three random points --- $\vec{\theta}_A$,
$\vec{\theta}_B$, and $\vec{\theta}_C$ --- and started all seven
methods at these points...

@@

Each of the parameter ??? methods was run on 3 different initial
parameter vectors, in order to fairly compare the algorithms. We allowed 
each run for the parameter ??? methods to
continue until the results plateaued (no improvement for one third of
the policies seen so far). Three runs of HyperNEAT were completed,
each with a different initial seed and run for 20 generations.

>>>>

\acmFig{linearInterp}{1}{To ensure fair fitness measurements, the
  position of the robot was measured at the beginning and end of each
  run in the same ``ready pose'' (\figref{robot_close.jpg}).  Motion
  was interpolated linearly between this stationary pose and the
  commanded gait g(t) for one second at the beginning of the run and
  two seconds at the end, as shown above.}

@@

@@
